High-Throughput-Derived Biologically-Inspired Features for Unconstrained Face Recognition

### 2011-12-06 discussion.tex
Add Sam's comments

While there still remains substantial room for improvement, concerns that
the \emph{LFW} set does not necessarily accurately reflect the ``full'' problem
of unconstrained face recognition
remain \cite{pinto:eccv08,pinto:cvpr09,kumar:iccv09}.  \emph{LFW} includes only
a handful of examples per individual, and these photographs were often taken in
the same setting and at the same event.  Furthermore, Kumar et
al. \cite{kumar:iccv09} showed that human observers were able to perform at
greater-than-90\% correct even when the faces themselves were masked out of the
test images, indicating that the backgrounds in the \emph{LFW} are more than
sufficient for solving the task at a level higher than the current machine state
of the art.

@@

As continued research manages to chip away at the remaining ``performance gap''
between human and machines on the \emph{LFW} set, increased attention will need
to be paid to whether \emph{LFW} truly represents the problem of interest.  On
one hand, as long as some performance gap exists, the set is obviously valid at
a basic level.  However, the question remains whether a ``fuller'' formulation
of the problem (i.e. more natural, less filtered) might lead to faster progress.

>>>>

While there still is substantial room for improvement, concerns remain that
the \emph{LFW} set does not necessarily accurately reflect the ``full'' problem
of unconstrained face recognition
\cite{pinto:eccv08,pinto:cvpr09,kumar:iccv09}.  \emph{LFW} includes only
a handful of examples per individual, and these photographs were often taken in
the same setting and at the same event.  Furthermore, Kumar et
al. \cite{kumar:iccv09} showed that human observers were able to perform at
greater-than-90\% correct even when the faces themselves were masked out of the
test images, indicating that the backgrounds in the \emph{LFW} are more than
sufficient for solving the task at a level higher than the current machine state
of the art.

@@

As continued research manages to chip away at the remaining ``performance gap''
between humans and machines on the \emph{LFW} set, increased attention will need
to be paid to whether \emph{LFW} truly represents the problem of interest.  On
one hand, as long as some performance gap exists, the set is obviously valid at
a basic level.  However, the question remains whether a ``fuller'' formulation
of the problem (i.e. more natural, less filtered) might lead to faster progress.

### 2011-12-06 ivcj_lfw.tex
Add Sam's comments

\title{
High-Throughput-derived Biologically-Inspired Features for Unconstrained Face Recognition
}

@@

\address[rowland]{The Rowland Institute at Harvard, Harvard University, Cambridge, MA 02142}
\address[mit]{McGovern Institute for Brain Science at MIT, Cambridge, MA 02139}

>>>>

\title{
High-Throughput-Derived Biologically-Inspired Features for Unconstrained Face Recognition
}

@@

\address[rowland]{The Rowland Institute at Harvard, Harvard University, Cambridge, MA 02142}
\address[mit]{McGovern Institute for Brain Research at MIT, Cambridge, MA 02139}

### 2011-12-06 results.tex
Add Sam's comments

To further explore the behavior of our models with a controlled stimulus, we examined model
performance as a function of the number of faces to be discriminated.  In particular, we
considered cases with two, four, six, and eight faces.  Performance, grouped by model is shown
in Figure \ref{fig:nfaces_by_model}, and is shown grouped by variation level in
Figure \ref{fig:nfaces_by_variation}.  Predictably, absolute performance level is depressed as a larger
number of faces is considered, as is the chance performance level (dotted line). Interestingly, the
rate at which performance falls off varies between models as a function of both number of faces
to be discriminated, and as a function of variation level.  The stability of the performance of the
largest/deepest model --- HT-L3-1st --- is most pronounced when large number of faces and large amounts of variation
are considered.  Differences between models are far less pronounced with smaller numbers of
faces and lesser degrees of variation.

>>>>

To further explore the behavior of our models with a controlled stimulus, we examined model
performance as a function of the number of faces to be discriminated.  In particular, we
considered cases with two, four, six, and eight faces.  Performance, grouped by model is shown
in Figure \ref{fig:nfaces_by_model}, and is shown grouped by variation level in
Figure \ref{fig:nfaces_by_variation}.  Predictably, absolute performance level is depressed as a larger
number of faces is considered, as is the chance performance level (dotted line). Interestingly, the
rate at which performance falls off varies between models as a function of both number of faces
to be discriminated, and as a function of variation level.  The stability of the performance of the
largest/deepest model --- HT-L3-1st --- is most pronounced when a large number of faces and large amounts of variation
are considered.  Differences between models are far less pronounced with smaller numbers of
faces and lesser degrees of variation.
